Illustrating Model Properties

### 2024-06-13 model.qmd
add missing imports

```{python}
import matplotlib.pyplot as plt
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import draw, COLORS, BetaPosterior
from lyscripts.compute.prevalences import compute_observed_prevalence
from scripts import paths, shared, COL
from scripts.marginalize_midext import (
  possible_prevalence_combinations,
  SummedBetaPosterior,
)

>>>>

```{python}
import matplotlib.pyplot as plt
import numpy as np
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import draw, COLORS, BetaPosterior
from lyscripts.compute.prevalences import compute_observed_prevalence
from scripts import paths, shared, COL
from scripts.marginalize_midext import (
  possible_prevalence_combinations,
  SummedBetaPosterior,
)
